\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{eurosym}
\usepackage{nth}
\usepackage{graphicx}
\usepackage[scale=0.75]{geometry}
\usepackage{import}
\usepackage{csquotes}
\name{Andreas}{Haupt}
\title{Curriculum Vit\ae}
%\address{Stockheimer Street 20}{Frankfurt, Germany}{}
%\phone[mobile]{+49 15739171484}
\email{haupt@mit.edu}
\homepage{indraos.github.io}
\social[linkedin][https://de.linkedin.com/in/andreas-haupt-273794b4]{andreas-haupt-273794b4}
\social[github][https://github.com/indraos]{indraos}
\begin{document}
\makecvtitle
\section{Education}
%\cventry{09/19-06/25}{PhD Social and Engineering Systems}{MIT}{}{}{}
\cventry{10/17-07/19}{B.Sc. Computer Science}{University of Frankfurt}{}{}{%
\begin{description}
	\item[Concentration] Probabilistic Machine Learning
\end{description}
}
\cventry{10/15-08/18}{M.Sc. Economics (excellent)}{University of Bonn}{}{GPA 3.74}{%
\begin{description}
	\item[Concentrations] Mechanism Design
	\item[Thesis] \enquote{Voting with Restricted Communication}
	\item[Supervisor] Dr. rer. pol. Benny Moldovanu
\end{description}}
\cventry{10/15-06/17}{M.Sc. Mathematics}{University of Bonn}{GPA 3.79}{}{{%
\begin{description}
	\item[Concentrations] Discrete Random Structures, Combinatorial Optimisation
	\item[Thesis] \enquote{A data Application of Graphon Theory}
	\item[Supervisor] Ngoc Mai Tran, PhD
\end{description}}}
\cventry{10/12-07/15}{B.Sc. Mathematics}{University of Bonn}{}{}{%
\begin{description}
	\item[Concentration] Discrete and Combinatorial Optimisation
\end{description}
}
\section{Professional Experiences}
\subsection{Professional}
\cventry{08/17-06/19}{Teach First Deutschland Fellow}{Vocational School}{Groß-Gerau}{}{%
\begin{description}
	\item[Courses taught] Mathematics, CS essentials (scratch, MIT AppInventor), Arduino
	\item[Training] Project management, instruction design, diversity, digital education
\end{description}}
\cventry{02/17-03/17}{Intern Scientific Assistance}{Member of German Parliament M. Wendt}{Berlin}{}{\begin{itemize}
	\item Conduct research on policy questions for homeland and digital policy matters
	\item Build a web scraper that saves 20min of download work each week
\end{itemize}}
\subsection{Academic}
\cventry{02/17-10/17}{Research Assistant}{Chair of Stochastic Analysis, University of Bonn}{}{}{%
%\begin{itemize}
%	\item {\LaTeX} and proof-read 2 research articles
%	\item Unify templates for several lecture notes (1200+ pages)
%\end{itemize}
}

\cventry{07/15-08/15}{Research Assistant}{Chair of Discrete Optimisation, EPFL}{Lausanne}{}{%
finish research semester project on maximisation of max-sum diversification.}



\section{Honours}
\cventry{03/13-07/17}{Full scholarship}{Evangelisches Studienwerk}{Schwerte}{1:100-competitive}{Evangelisches Studienwerk is one of 13 foundations giving academic state scholarships.}
\cventry{08/18-11/18}{Infrastructure Grant (\EUR{2000})}{State of Hesse}{Wiesbaden}{}{Install an Arduino Lab at Vocational School Groß-Gerau}
\cvitem{10/2018}{Win \nth{2} prize (\EUR{1500}) at Data Hackathon for NLP news relevance classification}
\section{Projects}
\cventry{11/18-06/19}{Data Ambassador}{Data Science for A Social Good}{Berlin}{\href{https://dssg-berlin.org/}{dssg-berlin.org}}{%
\begin{itemize}
	\item Improve and automise refugee-citizen matching algorithm for NGO \enquote{Start with a Friend}
\end{itemize}}
\cventry{10/17-06/19}{Scrum Master}{Bildungsfestival}{Essen}{\href{https://www.bildungsfestival.org/}{bildungsfestival.org}}{%
\begin{itemize}
	\item Introduce SCRUM to 20+ volunteer organisation for 100+ student networking event
\end{itemize}}


%\cventry{02/16-12/18}{Layout}{Brühwürfel Magazine}{Dortmund}{\href{mailto:bruehwuerfel.magazin@gmail.com}{bruehwuerfel.magazin@gmail.com}}{%
%\begin{itemize}
%	\item Transition Word-InDesign to Markdown-InCopy workflow.
%\end{itemize}}

%\cventry{01/18-06/19}{Strategy}{REDE.online}{Frankfurt}{\href{https://re-de.online/}{re-de.online}}{%
%\begin{itemize}
%	\item Create moderation concept and mockups for regional data/chat app
%\end{itemize}}
\cventry{02/17-11/17}{Organiser}{MLworkshopVilligst}{Tübingen}{\href{https://mlworkshopvilligst.wordpress.com/}{mlworkshopvilligst.wordpress.com}}{%
\begin{itemize}
	\item Organise machine learning workshop with 4 speakers from MPI-IS, 1 from Columbia
%	\item Help participants find a topic for 12 contributed talks and write blog entries
\end{itemize}}
\cventry{02/16-02/17}{Editor}{Bonn Journal of Economics}{Bonn}{\href{https://www.bje.uni-bonn.de/}{bje.uni-bonn.de}}{%
\begin{itemize}
%	\item Select 8 extended abstracts to appear in student journal
	\item Create new {\LaTeX} template still in use now
\end{itemize}}
\section{Presentations}
\cventry{04/18}{\href{https://www.mathematik.uni-muenchen.de/~hirsch/neuroConf/program2.html}{\enquote{Random Structures in Neuroscience and Biology}}}{LMU}{Munich}{}{}
\cventry{03/19}{Learning Video Production in Class}{Teacher candidate seminar}{Darmstadt}{}{Introduce apps (StopMotion Studio, Kinemaster + 4) and project management tools.}
\cventry{01/19}{---}{Regional Media Agency}{Frankfurt}{}{}
\cventry{04/19}{\enquote{Digital Participation Tools}}{Network interactive}{Frankfurt}{}{Present the use of online tools for seminar conception (Plickers, Polleverywhere + 5)}
\cventry{04/18}{---}{Ev. Akademie Villigst}{Schwerte}{}{}
\cventry{10/17}{\enquote{Intelligent Robots -- Simulation of Life?}}{Ev. Akademie Villigst}{Schwerte}{}{Give introduction to supervised learning and collaborative filtering for a general audience}


\section{Skills}
\cvitem{Tools}{pandas • sklearn • keras • C++ {\color{black!80} •} SQL • git • \LaTeX • Jekyll • Sketch • Adobe CS}
\cvitem{Languages}{German, English, French}
\section{Certifications}
\cvitem{Coursera}{Machine Learning (A. Ng, 09/17, 100\%), Deep Learning Specialisation (A. Ng, 10/17-02/18, 100\%), Neural Networks for Machine Learning (G. Hinton, 06/18, 99\%), Probabilistic Graphical Models: Representation (02/18, 96\%)}
\cvitem{Fobizz (German)}{App Development in Class • Teaching Programming using Scratch • Twitter Simply Explained • Learning Videos in Class • Using Greenscreen in Class}
\nocite{*}
\bibliographystyle{abbrv}
\bibliography{publications.bib}
\end{document}